---
title: "Weight of Fish"
author: "Leah Riganyan"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file="Fish.csv",header=TRUE)
```

## Perch
```{r}
Perch <- filter(fish, Species=="Perch")
Perch <- select(Perch, -(Species))
```

### Best Models

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
   
The best two regressor model is the one with height and width.   
      
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```   

The best model and the best two regressor model are the same

# Five Element Perch Model
```{r}
best_Perch_Model <- lm(Weight~Height+Width,data=Perch)
five_element_perch_model <- lm(Weight~.,data=Perch)
anova(best_Perch_Model, five_element_perch_model)
```
   
The variance table tells us there is not much difference compared to the five element model.

## Pike
```{r}
Pike <- filter(fish, Species=="Pike")
Pike <- select(Pike, -(Species))
```


### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```


### Best Two regressor model
```{r}
Pike_best.model <- lm(Weight~.,data=Pike)
summary(Pike_best.model)
Pike_best_2_R_model <- lm(Weight~Length1+Length3,data=Pike)
```   
      
Through an automated process, made several models.     
  
```{r}   
Pike_best.model <- lm(Weight~.,data=Pike)
Pike_best_2_R_model <- lm(Weight~Length1+Length3,data=Pike)
anova(Pike_best.model, Pike_best_2_R_model)
```
   
Anova gave us a p value that is .0 when comparing the two models. Since the p value is lower than .05, we can tell there's a significant difference between the two.
   
## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements